Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
UK spelling
Better looking table

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathtools}
\usepackage{coffee2}

@@

@@

\begin{enumerate}
\item Each skipper sails against each other skipper once.
\item When there is an even number of flights, each skipper has the same number
    of port and starboard assignments.
\item When there is an odd number of flights, the first half of the skippers
    will have one more starboard assignment.
\item No skipper in the last match of a flight should be in the first match of
    the next flight.
\item No skipper should have more than two consecutive port or starboard
    assignments.
\item Each skipper should be assigned to match 1, match 2, etc. in a flight as
    equally as possible.
\item In flights with five or more matches, no skipper should be in the
    next-to-last match in a flight and then in the first match of the next
    flight.
\item If possible, a skipper should be starboard when meeting the nearest
    lowest ranked skipper (i.e.\ \#1 will be starboard against \#2, \#3 will be
    starboard against \#4).
\item Close-ranked skippers meet in the last flight.
\item Minimize the number of boat changes.
\item Skippers in the last match of a flight do not change boats.
\item Skippers in new boats do not sail in the first match of the next flight.
\item Skippers have a reasonable sequence of matches and blanks.
\end{enumerate}

@@

\begin{table}[tb]
\begin{center}
\begin{tabular}{cc} \\
flight & matches \\ \hline
0 & (0,1) (2,3) (4,5)  \\
1 & (0,2) (4,6) (1,5)  \\
2 & (2,6) (0,5) (1,3)  \\
3 & (5,6) (0,3) (1,4)  \\
4 & (3,5) (1,6) (2,4)  \\
5 & (3,6) (0,4) (2,5)  \\
6 & (3,4) (1,2) (0,6)  \\ \hline
\end{tabular}
\end{center}
\caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights.
Skippers are numbered 0 to 6. Note that the order of skippers within a flight
is significant, as is position within a match (port or starboard). This
schedule is the result of stages 1 and 2, and has yet to be renumbered and
oriented (stages 3 and 4).}
\label{tab1}
\end{table}

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathtools}
\usepackage[rightcaption]{sidecap}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{coffee2}

@@

\sidecaptionvpos{table}{c}

@@

\begin{enumerate}
\item Each skipper sails against each other skipper once.
\item When there is an even number of flights, each skipper has the same number
    of port and starboard assignments.
\item When there is an odd number of flights, the first half of the skippers
    will have one more starboard assignment.
\item No skipper in the last match of a flight should be in the first match of
    the next flight.
\item No skipper should have more than two consecutive port or starboard
    assignments.
\item Each skipper should be assigned to match 1, match 2, etc. in a flight as
    equally as possible.
\item In flights with five or more matches, no skipper should be in the
    next-to-last match in a flight and then in the first match of the next
    flight.
\item If possible, a skipper should be starboard when meeting the nearest
    lowest ranked skipper (i.e.\ \#1 will be starboard against \#2, \#3 will be
    starboard against \#4).
\item Close-ranked skippers meet in the last flight.
\item Minimise the number of boat changes.
\item Skippers in the last match of a flight do not change boats.
\item Skippers in new boats do not sail in the first match of the next flight.
\item Skippers have a reasonable sequence of matches and blanks.
\end{enumerate}

@@

\begin{SCtable}[2.0][tb]
    \begin{tabular}{c@{\hspace{1.5em}}ccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (0,1) & (2,3) & (4,5) \\
        1 & (0,2) & (4,6) & (1,5) \\
        2 & (2,6) & (0,5) & (1,3) \\
        3 & (5,6) & (0,3) & (1,4) \\
        4 & (3,5) & (1,6) & (2,4) \\
        5 & (3,6) & (0,4) & (2,5) \\
        6 & (3,4) & (1,2) & (0,6) \\ \bottomrule
    \end{tabular}
    \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights.
        Skippers are numbered 0 to 6. Note that the order of skippers within a flight
        is significant, as is position within a match (port or starboard). This
        schedule is the result of stages 1 and 2, and has yet to be renumbered and
        oriented (stages 3 and 4).} \label{tab1}
\end{SCtable}
